The ideal description problem formulates the bridge between the abstract and machine world. It does this by concretizing the abstract concept of an ideal to a tangible set of generating polynomials that can be interacted with and evaluated. In order to bridge this gap, finite polynomials have to be found. Starting off with monomial ideals in $k[\vectorComponents{x}]$ is the best way to do so. 

Much like when introducing affine varieties, starting with a single monomial instead of the combination of them reduces complexity. So, when studying the ideals, we start with the same logic of considering a smaller problem. Consider the following defintion.

\begin{definition}
    An ideal $I \subseteq k[\vectorComponents{x}]$ is a monomial ideal that is determined by a set $A$ of integers. All polynomials in the ideal can be written as a linear combination of $\sum_{\alpha \in A} h_\alpha x^\alpha$ where $h_\alpha$ lies in $k[\vectorComponents{x}]$. 
\end{definition}

A quick tip when dealing with monomial ideals: they can largely be thought of as their exponents. This is their main benefit and why they are important when dealing with computer algebra systems. We will see this property shine in the comming proofs. As an example, consider the following lemma:

 \begin{lemma}
    Let $ I = \ideal{x^\alpha | \alpha \in A}$ be a monomial ideal. Then a monomial $x^\beta$ lies in $I$ if and only if $x^\beta$ is divisible by $x^\alpha$ for some $\alpha \in A$. 
 \end{lemma}

 \begin{proof}
    This can be proven by considering the exponents. Starting off with showing $x^\beta$ to $x^\alpha$, the exponents can be leveraged. If $\beta$ is a multiple of $\alpha$ then $x^\beta$ is in the ideal by definition since $x^\alpha$ generates the ideal. The other way around is slightly trickier. Using the definition of the monomial ideal, we can write $x^\beta$ as the polynomial sum of generators of the monomial idea and then write $ h_i$ as the sum of generators again.
     
 \begin{equation}
    x^\beta = \sum_{i = 1}^{s} h_i x^{\alpha(i)} = \sum_{i = 1}^{s}\bigg(\sum_{j}c_{i,j}x^{\beta (i,j)}\bigg)x^{\alpha(i)} = \sum_{i,j} c_{i,j}x^{\beta (i,j)}x^{\alpha(i)}
 \end{equation}

 Here we can see that every term on the right hand side is divisible by $x^\alpha$, so then $x^\beta$ on the left hand side must also be so. This proves that we can follow our intuition regarding the exponents and their divisibility much closer. After all, it goes both ways.

 \end{proof}

\subsubsection{Dicksons Lemma}
This lemma is really the meat of why we are interested in monomial ideals. The ability to reduce ideals to finite generators is the step towards closing the gap between the machine and abstract. 

\begin{theorem}
Let $I = \ideal{x^\alpha | \alpha \in A}$ be a monomial ideal. Then $I$ can be finitly written by $I = \ideal{x^{\alpha(1)}, ... , x^{\alpha(s)}}$, where all $\alpha$ lie in $A$.  
\end{theorem}

\begin{proof}
   The proof provided by the book \cite{Theory} takes an inductive approach. Starting off with $n=1$ for our $k[\vectorComponents{x}]$, it is easy to see that the smallest element of $A \subseteq \Z_{\ge 0}$ generates the remaining elements. When $n > 1$, the interesting part of the proof continues. Namely, we have the monomial ideal, call it $J$, from the $n-1$ case. This is finite by our induction, so when our $A$ goes from a subset of $\Z_{\ge 0}^{n-1}$ to $\Z_{\ge 0}^{n}$, we can generate slices of these $J$ ideals with the new $x_n = y$ variable. We take some sufficintly large $m \ge 0$ and group the $J_l$ ideals by their corrosponding $y$ value up to $m-1$. In other words, let the ideal $J_l$ be generated by $x^\beta$ where $x^\beta y^l \in I$. These $J_l$ slices form a "topological map" of the ideal $I$. Thus $I$ is also finite.    
\end{proof}

After a finite ideal is generated, the monomial ideal membership problem is solved. This is since we can take A polynomial and check if the remainder from division by the monomial ideal is $0$. If it is, it belongs to the monomial ideal.
