\clearpage{\thispagestyle{empty}}
\section{Introduction}

This bachelors thesis is centered around the intersection between theoretical mathematics and practical computer science: algorithms. Algorithms stand with one foot in each domain, and both are equally important. In order to begin instructing a computer on how to solve a problem, a clear idea of the problem as well as a concrete way to solve it must be established. This is the theoretical aspect of algorithmic construction and is agnostic of any computer implementation. Proving that a result is unique, or verifying that an algorithm terminates are critical aspects of success. The theoretical is not enough and one cannot avoid dirtying ones hands forever. The implementation is equally necessary. These algorithms are created to solve practical problems, and a way to use them is necessary.

The gap between the theoretical and practical is never easy to bridge. Especially since they both present unique challenges. The main algorithm being studied in this thesis is the construction of Gröbner bases. These bases are computationally useful and can be applied to optimizing the movement of robotic arms \cite{Applied}. As such, finding an algorithm that always yields a Gröbner basis and terminates after a finite number of steps is of interest. The steps taken to prove the algorithm theoretically were inspired by \cite{Theory}. After an understanding of the theory was present, the computer algebra system (CAS) Macaulay2 \cite{M2} was leveraged to implement the algorithm.

Division and polynomial elimination algorithms tackled through a different lens. Instead of standing in the middle, a step closer to the computer was taken. The thesis explores the process of receiving a proven algorithm and implementing it. The theory behind division algorithms is well known, and implementing them provided sufficient resistance when acclimating to a new computer language. When writing the division algorithms, the challenges were syntactical or a general lack of knowledge surrounding how a CAS works. The algorithms themselves are straightforward from a mathematical implementation view, but they were a necessary step to get accustomed with Macaulay2, these algorithms provided little mathematical insight. The implementation of the polynomial elimination provided a much needed step back towards the mathematical domain. Here, solid mathematical knowledge was necessary in order to inform the computer what had to be done. The pseudocode presented was more fluid and allowed for implementational flexibility. While this was an immense challenge, it was completed successfully.