\clearpage{\thispagestyle{empty}}
\section{The Algebreic Abstraction of Geometry}
Algebra is the mathematical expression of the human need for structure and abstraction. Through algebra, humans try to capture more of the mathematical, and natural, domain under their pen. The endless hunger for knowledge can express itself in various way. When using algebra as a tool, creating abstract models that capture generic structure is favored. However, these abstract models can be difficult to understand. The ability to navigate between levels of abstraction is a vital tool for any mathematician interested in applying algebreic methods. 

This paper assumes a degree of familiarity with algebreic structures, but the uninitiated peruser is kindly directed towards the easy-going introduction of "Introducetion to Modern Algebra" \cite{weiner1970introduction} with bite size exercises, or alternativly, the more rigorous "Abstract Algebra" \cite{dummit2003abstract} for a deeper understanding. 

As the section header suggests, this section will be primarily focused with defining the tools necessary to build an analytic bridge between geometry and algebra so that we can analyze geometric objects with algebra. A function that maps geometric objects to algebreic must be established. This function uses Affine Varietes and Ideals, along with the dictionary established in the Hilbert Strong Nullstellensatz, to accomplish that goal.

\subsection{Levels of Abstraction}
\input{subsections/LevelsOfAbstraction.tex}

\subsection{Polynomials}
\input{subsections/Polynomials.tex}

\subsection{Affine Spaces and Varieties }
\input{subsections/AffineVarieties}

\subsection{Rings and Ideals}
\input{subsections/RingsAndIdeals}

\subsection{Ordering Polynomials}
\input{subsections/OrderingPolynomials}

\subsection{An Analytic Bridge}
\input{subsections/AnAnalyticBridge}

\subsection{Hilbert Strong Nullstellensatz}
\input{subsections/HilbertStrongNullstellensatz}