\clearpage{\thispagestyle{empty}\cleardoublepage}

\section{Discussion}
There are two distinct parts of this thesis to consider: the construction of an algorithm and the execution of an algorithm. They were not weighed equally in this thesis. This section considers the imbalance between the two and what they offered as part of a thesis surrounding mathematics.

\subsection{Mathematical Proof and Knowledge}
Building an algorithm requires intimate knowledge of underlying mathematical concepts as well as a familiarity with proof construction. While background knowledge was gathered for affine varieties, and more generally algebraic geometry, these were less significant to the scope of the thesis. Instead, these concepts justified the exploration of Gröbner bases. Even then, theory surrounding the \textit{usage} of Gröbner bases was limited. Instead, a majority of the theoretical knowledge and proofs found in the thesis concern Gröbner bases, specifically the construction of the Buchberger criterion. The criterion is the motor behind the Buchberger algorithm, used to constructs Gröbner bases, and provided deep insight into how algorithms are created.

Singling in on the Buchberger criterion left other parts of the mathematical domain unexplored. Especially when it comes to the Gröbner bases usefulness. The  elimination properties of the bases and any application to algabraic geometry or robotics were left unexplored. Both the topics are interesting in their own regard, and future work surrounding the subject would do well to engage with them in greater detail. 

\subsection{Algorithm Implementation} 
The traditional mathematical method of proving theorems was less important in the creation of this thesis. Instead the primary focus was directed towards the implementation of algorithms. While an impressive part of algorithms is transforming an idea to something concrete, another is to implement the algorithm itself. For a bachelors thesis, the implemention felt appropriate. Familiarizing oneself with the process of algorithm construction was of importance but exploring the the implementation was more fruitful from a learning aspect. Abstract algebra can be confusing, and having concretizing concepts so a machine can execute the algorithm increased understanding of the underlying objects. Learning a computer language where ideals are an integral reason to its creation is bound to provide deeper insight into ideals themselves. To use ideals and rings, one must have a working knowledge of them.

Through implementation, the balacing act between the amount of work that is necessary to create these algorithms and keeping the implementation simple can be appreciated. The Buchberger algorithm is reduced to concrete steps, such as finding S-polynomials \ref{def:spolynomial}, but proving that the Buchberger criterion is sufficient for Gröbner basis is involved. In contrast, the algorithm that finds the solution to polynomial systems (listing \ref{lst:algorithm161}) provides guidelines and is flexible in its interpretation; it shifts more responsibility to the implementee. 
