The order of the dividing polynomials affects the outcome when performing multivariate division. This is problematic when when establishing deterministic outcomes. By fixing a lexographical order, Gröbner bases gaurantee a unique remainder. 

\begin{proposition}
    Let $I \subseteq \polyRing$ be an ideal and let $G =  \lbrace \vectorComponentsX{g}{t} \rbrace$ be a Gröbner basis for $I$. Then given $ f \in \polyRing$, there is a unique $r \in  \polyRing$ with the two following properties:
    
    \begin{enumerate}
        \item No term of r is divisible by any of $LT(g_1), ... , LT(g_t)$.
        \item There is a $g \in I$ such that $f = g + r$.
    \end{enumerate}

    \begin{proof}
        Consider the division algorithm $f = q_1 g_1 \dots + q_n g_n + r $. Every $LT(g_t)$ is already divided out. In other words, if r had been divisible by the lead term there would have been a corrosponding $q_t$ to engulf it. That proves $(1)$. $(2)$ is solved by considering the fact that we are operating with Gröbner bases; we must leverage our ability to show that $\specialGrobCondition$. To prove uniqueness, assume that the remainder is non-unique and use lemma \ref{lemma:4-2} to disprove that assumption. In other words: assume that $f = g + r = g' + r'$ follows our proposition. Rearranging, $r-r'= g-g'\in I$. Now, using the special property of the basis, $LT(r-r') \in \specialGrobCondition$. Since $LT(r-r')$ is on $LT(g_i)$, then it is also divisible by that same $LT(g_i)$. Using the first property, $r - r'$ cannot be divided by $LT(g_i)$, so in order for the division to succeed, $r - r' = 0$. This contradicts the assumption that $r$ was non-unique.   
    \end{proof}
\end{proposition}

Another important property is how easily one can verify if a function is in an ideal. The membership problem is solved by dividing $f$ by $G$ and checking if the remainder is zero. If it is, then the function belongs to the ideal. This membership check's concrete nature is useful for computational applications. 