Division algorithms have been of interest to mathematicians for a long time. Euclid's algorithm, one of the oldest algorithms created, has applications to division as well. Basic arithmetic with addition, subtraction, and multiplication can be constrained to $\Z$, the integers, while the introduction of division necessitates an entirely different way of interacting with numbers, $\Q$, the rationals. Division is useful, so a mathematical programming language must be equipped with ways to handle it. Macaulay2 has various ways of dividing, but attempting to extend it to divide polynomials left me with a multitude of problems, highlighting how complicated algebra can actually be. 

\subsubsection{Univariate Division Algorithm}
\label{sssec:univariate-division-algorithm}
The first algorithm I tried writing was \ref{lst:algorithm121}. This is basic univariate polynomial division, something that most high schoolers learn. The algorithm is rather simple. Take the leading term of the numerator and divide it by the denominator. Add the quotient to the result and subtract the quotient times the denominator from the numerator. Repeat until the numerator is zero or the degree of the denominator exceeds that of the numerator. None of the ordering issues or really anything at all is difficult in this case. The built in division operator works without any issues. Filled with confidence, the multivariate algorithm was attempted. 

\subsubsection{Multivariate Division Algorithm}
\label{sssec:multivariate-division-algorithm}
The idea behind the multivariate division algorithm is not much different from the univariate one. Divide a polynomial $p$ by an array of polynomials $gs$. If the leading term of $p$ cannot be divided by the leading term of the first polynomial of $gs$, move on to the next until one that can is found. If no leading term of $gs$ can divide the leading term of $p$, then the leading term is subtracted from $p$ and the algorithm marches to the next polynomial. This seems easy enough, but there is quite a lot of complexity hiding between the lines. The first complexity had to do with the fact that there are more dimensions. Dividing with one dimension is easy enough, but when more are introduced, a way to organize the different dimensions is required. MonomialOrdering is introduced to solve this problem. 

Another issue was how to divide the leading monomials. With the addition of higher dimensions, the regular division was giving fractions of rings. This is an issue because the algorithm wants to remain within the ring itself, not outside of it. Foolishly, I decided to try and create a leadingTermDivision function that decomposed the polynomials into lists of monomials, coefficients, and exponents. The idea was simple. Macaulay2 generates a list of the exponents, taking the ring elements into account. So if the ring is $Q[x,y,z]$, the polynomial $x^2*z$ would be decomposed into $\{2,0,1\}$. By creating these lists and subtracting the exponents from each other, the division has occurred. All that would be left would be to recreate the polynomial using the generators of the ring and raise them to the exponent in the listed order. However, here my lacking understanding of Macaulay2 and, more generally, ring algebra can be seen. The generators of the ring and the ring itself are different. In line 63 of \ref{lst:algorithm123}, toList gens ring $p$ is used. Here, we find the ring of the polynomial $p$, find the generators of the ring, and then create a list of them. However, when later applying the exponential list to the generators, the returned polynomial is not an element of the ring that the function caller is using; it simply has the same variables. 

Instead of recreating a way to divide monomials or using fractions of rings, there is a division that ensures the result remains in the ring. It does so by using division with remainder. With this realization, the algorithm was ready to be implemented. By first checking whether the modulo of the leading monomial would be $0$, we can ensure that the ring division would not produce a remainder. So if the modulo did produce a remainder, the next $gs$ was considered. If there was no remainder, essentially the univariate case was established.

One important note here is that, as another reason to use Gröbner bases, the order of the polynomials sent in, $gs$, matters significantly. Different orderings of the $gs$ list generate different results. A test showing this can be found in \ref{lst:algorithm123}. Gröbner bases eliminate this reliance on the order, which is desirable.