
After installing the Windows Subsystem for Linux, the Macaulay2 (M2) playground was ready and open. Since the main book \cite{Applied} I was using had an introductory section to the language, the first order of business was to familiarize myself with EMACS and how the syntax of the language worked. This took quite some time as EMACS/Linux is highly unfamiliar to me and the syntax used when interfacing with the M2 console line is different from when one writes a script. 

The very first script I wrote, \ref{lst:book-example-2-1-1} mirrors this confusion. Even though I am creating a script. Double $*$ are being used instead of exponentials because the swedish keyboard has an odd knack for making the powers small. This lead to compiler mismatches and wasted hours. This script is a starting point in how to use the language. Important features such as which ring is being operated upon, which ordering, and how to create a Gröbner basis is touched upon. The next couple of book examples, namely \ref{lst:book-example-2-2} and \ref{lst:book-example-222} show how to construct more involved rings as well as how to evaluate functions in the ring itself. This eased the understanding of how to use rings in the language.

While helpful, these book examples provided little help in how to construct a script that executes any sort of meaningful code. The book displayed clips from the command line of M2, which is not the proper format for writing algorithms. So even though book example \ref{lst:book-example-2-1-1} and \ref{lst:book-example-231} show built in ways to perform division and find the remainder, implementing a division algorithm in one and multiple dimensions seemed like an appropriate start to acclimate myself to the language.


